Enhancing Autonomy of Mobile Robots with Behavior Tree using ROS2

### 2023-02-01 Paper/paper.tex
updated email adresses
Minor title modification before submission

\title{Enhancing Autonomy of Mobile Robots with Behavioral Tree using ROS2}

\author{Lukas Evers$^{*,1}$, Umut Uzunoglu$^{1}$, and Ahmed Hussein$^{1}$ \textit{Senior Member, IEEE}%
    \thanks{$^{*}$ Corresponding author }%
    \thanks{$^{1}$ IAV GmbH, Berlin, Germany \newline
		{\tt\small lukas.evers@iav.de, umut.uzunoglu@iav.de, ahmed.hussein@ieee.org}}%
}

>>>>

\title{Enhancing Autonomy of Mobile Robots with Behavior Tree using ROS2}

\author{Lukas Evers$^{*,1}$, Umut Uzunoglu$^{1}$, and Ahmed Hussein$^{1}$ \textit{Senior Member, IEEE}%
    \thanks{$^{*}$ Corresponding author }%
    \thanks{$^{1}$ Digital Lab, IAV GmbH, Berlin, Germany \newline
		{\tt\small lukas.e@web.de, umutuzunoglu@hotmail.de, ahmed.hussein@ieee.org}}%
}
